Ce que j'ai compris jusqu'à maintenant\\Début de rapport ?

### 2025-04-09 article_bihom_v2.tex
ajout compréhension papier FSS

		\begin{theorem}[Theorem 2 in \cite{FSS11}]
			Let $i > n_x + 1$ (resp. $i > n_y + 1$) and let $s$ be a linear combination of maximal minors of $jac_{x}(F_{i-1})$ (resp. $jac_{y}(F_{i-1})$). Then $s \in I_{i-1} : f_i$
		\end{theorem}

@@

>>>>

		\begin{theorem}[Theorem 2 in \cite{FSS11}]\label{theoremMaxMin}
			Let $i > n_x + 1$ (resp. $i > n_y + 1$) and let $s$ be a linear combination of maximal minors of $jac_{x}(F_{i-1})$ (resp. $jac_{y}(F_{i-1})$). Then $s \in I_{i-1} : f_i$
		\end{theorem}

@@

		As theorem \ref{theoremMaxMin} indicates, reductions to 0 can also arise from the maximal minors of the jacobian matrix, so the signatures ($s, f_i$) where $s$ is a linear combination of maximal minors of $jac_{x}(F_{i-1})$ or $jac_{y}(F_{i-1})$ is a reduction to 0.
		This explains Algorithm \ref{alg:crit_calc} where we compute the maximal minors the jacobian matrices before applying Algorithm \ref{alg:reduc} where we compute linear combinations of these maximal minors.
		This means that Algorithm \ref{alg:crit_calc} computes all the signatures that will arise in reductions to 0 that involve the maximal minors of jacobian matrices instead of being incremental like F5 criterions \cite{F02}.
